---
title: "Vignette Title"
author: "Vignette Author"
date: "`r Sys.Date()`"
output: rmarkdown::github_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```
# JSON data description
  
  **JSON** (JavaScript Object Notation) is a lightweight and flexible data format that is easy for humans to read and for machines to parse. JSON has become a common format used in: 
  
  * Public APIs (e.g., Twitter)
  * NoSQL databases as a document format (e.g., MongoDB)
  * Relational databases as a new column type (e.g., PostgreSQL)
  
  
  
  More information can be checked [here](https://en.wikipedia.org/wiki/JSON) and JSON syntax introduction is [here](http://json.org/)
  
  [JSON (JavaScript Object Notation)](https://en.wikipedia.org/wiki/JSON) is an open standard file format, originally specified by [Douglas Crockford](https://en.wikipedia.org/wiki/Douglas_Crockford). It is commonly used for exchanging data in web applications. JSON uses human-readable syntax and is a programming language-independent format. File in JSON format can be easily checked manually using text editors or processed to extract information with many different packages/tools, so JSON is also a very good choice for storing data.
  
# Ways to read JSON data into R

  






You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
